Lattice Boltzmann simulations of magnetically responsive\\ anisotropic particle stabilized emulsions

### 2025-02-16 chapters/paper2.tex
Changes 1. Added more analysis to application of magnetic fields during formation chapter 2. Added references to fix some (not all) literature reference issues 3. Added some detail in analysis techniques section

\section{Introduction}
\section{Results}\label{sec:results_p2}

@@

Before the structure factor was calculated, the location of the particles were filled with the average density of the 
surrounding lattice sites using Equation \ref{eq:fill_particles} to generate a smooth interface. The particles are 
iteratively filled from outside in until all lattice points corresponding to the particle are filled with the average 
density of the fluid surrounding the lattice point. Within the red and blue fluid densities, sites representing the 
particles are filled before the order parameter is calculated. By filling the particles, we are able to analyze the 
microstructure without the influence of the particles. We calculate the hysteresis curve by calculating the domain 
size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the 
differences observed. We plot these results in Figure \ref{fig:hysteresis_curve}

\begin{figure} 
    \centering 
    \includegraphics[scale=0.7]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Hysteresis curve of bijels stabilized with magnetically responsive ellipsoidal particles. The y-axis is the average length scale $\frac{L}{R}$ normalized with the radius of the particle, while the x-axis corresponds to the dimensionless magnetic field strength $\bar{B}$. We show that there is domain coarsening upon increase of the field strength, followed by jamming of the structure as the field strength is decreased indicating the path dependence of the bijel microstructure.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.7]{../figures/results/paper2/microstructure_viz-field_on.png} 
    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). The top 
            column demonstrates the microstructure evolution if no field is used while the bottom column demonstrates 
            the microstructure evolution when the system is exposed to a field strength of $\bar{B} = 1$. Particle 
            reorientation to the direction of the field can be seen, resulting in microstructure changes driven 
            through domain coarsening until the particles jam.} 
    \label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.7]{../figures/results/paper2/domain_size-field_on.png} 
    \caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the 
             particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
             We quantify the domain size and ordering of the particles, and show that the change in both parameters
            are correlated with the strength of the applied magnetic field.} 
    \label{fig:domain_size-field_on} 
    \end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on 
             the left and right respectively for bijels stabilized with magnetically responsive prolate ellipsoids. 
             We see that upon application of the field, the domain size parallel to the applied field direction, 
             $L_{\parallel}$ increases while the domain size perpendicular to the applied field, $L_{\perp}$ decreases.
             These results support the tortuosity data obtained which show that $\tau_{\parallel}$ decreases, 
             indicating a shorter path length, while $\tau_{\perp}$ increases, indicating a longer path length.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.7]{../figures/results/paper2/particle_viz-field_on.png} 
    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). 
            The top column demonstrates the microstructure evolution if no field is used while the bottom column 
            demonstrates the microstructure evolution when the system is exposed to a field strength of $\bar{B}_z = 1$. 
            Particle reorientation to the direction of the field can be seen, resulting in coarsening of the domains.} 
    \label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics{../figures/results/paper2/domain_size-field_on-scaled.png} 
    \caption{Plots of domain size with different timescales. The figure on the left rescales time with the nematic to 
            isotropic transition time while the figure on the right rescales time with the time taken till the 1st minimum in 
            the interface angle is reached. We show that the controlling timescale when applying a magnetic field onto bijels 
            with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance as the 
            interface is dragged along with the particles upon reorientation.} 
    \label{fig:domain_size-field_on-scaled} 
\end{figure}

>>>>

\section{Results}\label{sec:results_p2}

@@

Before the structure factor was calculated, the location of the particles were filled using the procedure detailed in
Section \ref{section:filling_routine} to generate a smooth interface. By filling the particles, we are able to analyze the 
microstructure without the influence of the particles. We calculate the hysteresis curve by calculating the domain 
size at the final timestep of each magnetic field change. We then plot these domain sizes against the magnetic field 
applied to obtain them and split them in the descending and ascending magnetic field directions to demonstrate the 
differences observed. We plot these results in Figure \ref{fig:hysteresis_curve}

\begin{figure} 
    \centering 
    \includegraphics[width=\textwidth]{../figures/results/paper2/hysteresis_curve.png} 
    \caption{Hysteresis curve of bijels stabilized with magnetically responsive ellipsoidal particles. The y-axis is the average length scale $\frac{L}{R}$ normalized with the radius of the particle, while the x-axis corresponds to the dimensionless magnetic field strength $\bar{B}$. We show that there is domain coarsening upon increase of the field strength, followed by jamming of the structure as the field strength is decreased indicating the path dependence of the bijel microstructure.} 
    \label{fig:hysteresis_curve} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{../figures/results/paper2/microstructure_viz-field_on.png} 
    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). The top 
            column demonstrates the microstructure evolution if no field is used while the bottom column demonstrates 
            the microstructure evolution when the system is exposed to a field strength of $\bar{B} = 1$. Particle 
            reorientation to the direction of the field can be seen, resulting in microstructure changes driven 
            through domain coarsening until the particles jam.} 
    \label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size-field_on.png} 
    \caption{Plotting the spherically averaged domain size normalized with $R_p$($L/R$) of the 
             particle at different magnetic field strengths, $\bar{B}$, and the nematic order parameter $S$ in lines.
             We quantify the domain size and ordering of the particles, and show that the change in both parameters
            are correlated with the strength of the applied magnetic field.} 
    \label{fig:domain_size-field_on} 
    \end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on 
             the left and right respectively for bijels stabilized with magnetically responsive prolate ellipsoids. 
             We see that upon application of the field, the domain size parallel to the applied field direction, 
             $L_{\parallel}$ increases while the domain size perpendicular to the applied field, $L_{\perp}$ decreases.
             These results support the tortuosity data obtained which show that $\tau_{\parallel}$ decreases, 
             indicating a shorter path length, while $\tau_{\perp}$ increases, indicating a longer path length.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{../figures/results/paper2/particle_viz-field_on.png} 
    \caption{Visualizations of bijels simulated under no fields at $t = 0$ (left) and $t = 10^5$ (right). 
            The top column demonstrates the microstructure evolution if no field is used while the bottom column 
            demonstrates the microstructure evolution when the system is exposed to a field strength of $\bar{B}_z = 1$. 
            Particle reorientation to the direction of the field can be seen, resulting in coarsening of the domains.} 
    \label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[width=\columnwidth]{../figures/results/paper2/domain_size-field_on-scaled.png} 
    \caption{Plots of domain size with different timescales. The figure on the left rescales time with the nematic to 
            isotropic transition time while the figure on the right rescales time with the time taken till the 1st minimum in 
            the interface angle is reached. We show that the controlling timescale when applying a magnetic field onto bijels 
            with disordered particles is the latter timescale, indicating that the dominating effect is steric hindrance as the 
            interface is dragged along with the particles upon reorientation.} 
    \label{fig:domain_size-field_on-scaled} 
\end{figure}
